### 2019-05-19 README.rmd

*Rclean* usage is simple. Have a script with code you want to clean
saved to disk.

Once you have your script and workspace setup, you can use
[Rclean](https://github.com/ProvTools/Rclean) to get clean chunks of a
larger script that produce specific results you want. We'll use the
micro.R script, which can be found inside the package repo in the
*exec* directory. The following example assumes that your current
working directory is *exec*.

First, you'll need to record information about the script you would
like to parse. [Rclean](https://github.com/ProvTools/Rclean) uses data
provenance to verify what lines of code depend on each other inside of
the larger script. We can use the
[provR](https://github.com/ProvTools/provR) package to generate
provenance. The next bit of code runs our script and saves the
provenance to memory, which we then pass to the `options` function, so
that [Rclean](https://github.com/ProvTools/Rclean) has access to it:

```R
prov.capture("micro.R")
options(prov.json = prov.json())
```

Or, if you have provenance saved as a text file, you can load it in
like this:

@@

Now that we have the provenance loaded, we can start
cleaning. [Rclean](https://github.com/ProvTools/Rclean) will give us a
list of possible values we can get code for:

```R
clean()

@@

You can then pick and choose from among these results and get the
essential code to produce the output, like so:

```R
clean(x)

Notice that the 'clean' function doesn't require you to quote your
results, it interprets all inputs as names of results.

In many cases, it's handy just to take a look at the isolated code,
but if you can also save the code for later use or sharing.

```R
my.code <- clean(x)
write.code(my.code, file = "x.R")

If you would like to copy your code to the clipboard, you can do that
by not specifying a file path.

```R
write.code(my.code)

>>>>

*Rclean* usage is simple. Have a script with code you want to clean
saved to disk. Then, just run the `clean` function with the path to
the script as the input:

```
clean("./example/simple_script.R")
```

This returns a list of possible results detected in the script,
including execution lines (not counting lines with no code or that are
commented). We can now pick the result we want to focus on for
cleaning:

```
clean("./example/simple_script.R", "tab.15")
```

This produces the minimal code detected from the script. It also
detects the package dependencies as well and provides them in the code
(`libs = TRUE`).

It can be handy just to take a look at the isolated code, but you can
save the code for later use or sharing (e.g. creating a reproducible
example for getting help) with the `write.code` function:

```
my.code <- clean("./example/simple_script.R", "tab.15")
write.code(my.code, file = "x.R")
```

If you would like to copy your code to the clipboard, you can do that
by not specifying a file path. You can now paste as needed to create a
simpler script.

```R
write.code(my.code)
```

## Retrospective Provenance

So far, we've been using "prosepctive" provenance generated from the
static code prior to execution. *Rclean* can also be used with
"retrospective" provenance, which is recorded during execution of a
script. To do so, we can pass the provenance to the `clean` function
via `options`:

@@

Now that we have the provenance loaded, we can start
cleaning. [Rclean](https://github.com/ProvTools/Rclean) will give us a
list of possible values we can get code for, notice that the option
*rp* (i.e. "retrospective provenance") has been set to `TRUE`:

```R
clean(rp = TRUE)

@@

Similar to before, you can then pick and choose from among these
results and get the essential code to produce the output, like so:

```R
clean(x, rp = TRUE)
